Paper 1: Vitis

### 2018-02-06 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
library(tidyverse)
```

>>>>

```{r}
library(tidyverse)
library(readxl)
read_excel("R_DiLP_all_species.xlsx")
read_excel("R_DiLP_Vitis_all_added.xlsx")
```

# t-tests
First, we tested whether there were significant differences between the two growing seasons for each of the ratios measured, as well as the total number of teeth. To do this, we ran a series of t-tests.
